First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-05-03 eg6-letters/coherent/dvcs_he4_prl.tex
dvcs_he4_prl.tex:  add mohammad thesis

%DVCS selection
To identify coherent DVCS events, we first select events where one electron, 
one $^4$He, and at least one photon are detected in the final state. Electrons 
are identified using their measured momentum, time, and energy obtained from 
the CLAS drift chambers, Cerenkov counters, scintillator counters, 
and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
the RTPC using time, track quality, and energy-loss cuts for tracks in the 
fiducial region. In addition, we apply a vertex-matching cut to ensure that the 
electron and helium nucleus originate from a common reaction vertex in the target cell. The photons are 
detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. Indeed,
soft photons are produced at very high rates by the electron beam and create 
numerous accidental coincidences. These do not affect directly our mesurement, 
where only the most energetic photon is considered as DVCS photon candidate.
This prescription however slightly increases the corrections associated with
the $\pi^0$ and the accidental backgrounds discussed below.

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}$ greater than 1 
GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle ($\Delta\phi$) between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
between the measured photon and the missing momentum of the $e'^4$He$'$ system.

The experimental data for the most relevant observables and applied
cuts is shown in Fig.~\ref{fig:kin-cuts}.
%The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
%shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
%large and for which we reduced the cut window to [-0.45,0.5] GeV).
We also 
reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
two photons. About 3200 events pass these requirements. Their kinematic 
distributions are shown in Fig.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the coherent DVCS events candidates. The shaded 
distributions represent the events which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied exclusivity 
cuts. The distributions from left to right and from top to bottom are: $\Delta 
\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
between the measured and the calculated photon.}
\label{fig:kin-cuts}
\end{figure}

@@

>>>>

%DVCS selection
To identify coherent DVCS events, we first select events where one electron, 
one $^4$He, and at least one photon are detected in the final state. Electrons 
are identified using their measured momentum, time, and energy obtained from 
the CLAS drift chambers, Cerenkov counters, scintillator counters, 
and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
the RTPC using time, track quality, and energy-loss cuts for tracks in the 
fiducial region \cite{Hattawy:thesis}. In addition, we apply a vertex-matching cut to ensure that the 
electron and helium nucleus originate from a common reaction vertex in the target cell. The photons are 
detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. Indeed,
soft photons are produced at very high rates by the electron beam and create 
numerous accidental coincidences. These do not affect directly our mesurement, 
where only the most energetic photon is considered as DVCS photon candidate.
This prescription however slightly increases the corrections associated with
the $\pi^0$ and the accidental backgrounds discussed below.

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}$ greater than 1 
GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle ($\Delta\phi$) between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The experimental data for the most relevant exclusivity observables and applied
cuts is shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details).
%The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
%shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
%large and for which we reduced the cut window to [-0.45,0.5] GeV).
We also 
reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
two photons. About 3200 events pass these requirements, and their kinematic 
distributions are shown in Fig.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the initial candidate events, while the shaded 
distributions represent those which which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied cuts.
The distributions from left to right and from top to bottom are: $\Delta 
\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
between the measured and the calculated photon.}
\label{fig:kin-cuts}
\end{figure}

@@

\bibitem{Hattawy:thesis}
M.~Hattawy, Ph.D. thesis, Universit{\'e} Paris Sud - Paris XI, France 
[Institution Report No. 2015PA112161].
